---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# KinaseTauScore

<!-- badges: start -->

[![GitHub issues](https://img.shields.io/github/issues/CogDisResLab/KinaseTauScore)](https://github.com/CogDisResLab/KinaseTauScore/issues) [![GitHub pulls](https://img.shields.io/github/issues-pr/CogDisResLab/KinaseTauScore)](https://github.com/CogDisResLab/KinaseTauScore/pulls)
[![R-CMD-check](https://github.com/CogDisResLab/KinaseTauScore/workflows/R-CMD-check/badge.svg)](https://github.com/CogDisResLab/KinaseTauScore/actions)
[![BiocCheck](https://github.com/CogDisResLab/KinaseTauScore/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/CogDisResLab/KinaseTauScore/actions)

![GitHub release (latest SemVer)](https://img.shields.io/github/v/release/CogDisResLab/KinaseTauScore)
![GitHub release (latest SemVer including pre-releases)](https://img.shields.io/github/v/release/CogDisResLab/KinaseTauScore?include_prereleases)
![GitHub](https://img.shields.io/github/license/CogDisResLab/KinaseTauScore)

[![BioC status](http://www.bioconductor.org/shields/build/release/bioc/KinaseTauScore.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/KinaseTauScore)
[![Codecov test coverage](https://codecov.io/gh/CogDisResLab/KinaseTauScore/branch/main/graph/badge.svg)](https://app.codecov.io/gh/CogDisResLab/KinaseTauScore?branch=main)

<!-- badges: end -->

`KinaseTauScore` is a data package that allows access to a curated dataset of phsophorylation profiles of human kinases on the 𝛕-protein in an Alzhemier Disease context. The data is derived from the paper `High-content siRNA screening of the kinome identifies kinases involved in Alzheimer's disease-related tau hyperphosphorylation` by Azorsa et al[^1].

[^1]:
    Azorsa DO, Robeson RH, Frost D, et al. High-content siRNA screening of the kinome identifies kinases involved in Alzheimer’s disease-related tau hyperphosphorylation. BMC Genomics. 2010;11(1):25. <doi:10.1186/1471-2164-11-25>

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install `KinaseTauScore` from [Bioconductor](http://bioconductor.org/) using the following code:

```{r 'install', eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install("KinaseTauScore")
```

And the development version from [GitHub](https://github.com/CogDisResLab/KinaseTauScore) with:

```{r 'install_dev', eval = FALSE}
BiocManager::install("CogDisResLab/KinaseTauScore")
```

## Citation

Below is the citation output from using `citation('KinaseTauScore')` in R. Please run this yourself to check for any updates on how to cite **KinaseTauScore**.

```{r 'citation', eval = requireNamespace('KinaseTauScore')}
print(citation('KinaseTauScore'), bibtex = TRUE)
```

Please note that the `KinaseTauScore` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `KinaseTauScore` project is released with a [Contributor Code of Conduct](https://bioconductor.github.io/bioc_coc_multilingual/). By contributing to this project, you agree to abide by its terms.

## Development tools

-   Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/) through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
-   Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
-   The [documentation website](http://CogDisResLab.github.io/KinaseTauScore) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
-   The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
-   The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.
